---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(ggplot2)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggdebug

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of ggdebug is to make it easier to debug functions and ggproto methods in ggplot2.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/ggdebug")
```

If you can load the package, you're all set!

```{r}
library(ggdebug)
```

## Debugging

Use `ggdebug()` to debug functions (they can be exported, non-exported, or `ggproto` methods), use `ggundebug()` to stop debugging specific functions, and use `ggundebug_all()` to stop debugging altogether.

```{r example, eval = FALSE}
# debug ggplot() and GeomPoint$draw_panel()
ggdebug(ggplot, GeomPoint$draw_panel)

# stop debugging functions
ggundebug(ggplot)

# stop debugging all functions
ggundebug_all()
```

You can also use this package to install specific versions of ggplot2 from GitHub that link back to the source:

```{r}
# gginstall("cran/ggplot2")
# gginstall("tidyverse/ggplot2@v3.1.1")
(ggbrowse(FacetWrap$map_data))
```

## Tracing

Use `ggtrace()` (and family) to evaluate abitrary code as functions enter an exit. `ggtrace_tree()` and `ggtrace_stack()` are useful shortcut methods.

```{r, fig.show='hide'}
ggtrace(FacetWrap$map_data, on_enter = quo(print(data)), on_exit = quo(print(data)))
ggplot(mpg, aes(cty, hwy)) + geom_point() + facet_wrap(vars(class))
gguntrace(FacetWrap$map_data)
```


```{r, fig.show='hide'}
ggtrace_tree(
  FacetWrap$map_data, 
  FacetWrap$compute_layout,
  combine_vars,
  eval_facets
)

ggplot(mpg, aes(cty, hwy)) + geom_point() + facet_wrap(vars(class))
gguntrace_all()
```

## Helpers

More than likely, you'd like to debug an entire ggproto class. For this you can use `ggmethods()` and the splice to debug many functions at once.

```{r, fig.show='hide'}
ggtrace_tree(!!!ggmethods(FacetWrap))
ggplot(mpg, aes(cty, hwy)) + geom_point() + facet_wrap(vars(class))
gguntrace_all()
```
